% Paul Pham's Curriculum Vitae

\documentclass[letter]{article}
\usepackage{fancyhdr}
\usepackage[osf]{mathpazo}
\usepackage{lastpage}
\usepackage[pdftex]{graphicx,color,hyperref}
\usepackage{url}

\newcommand{\customfoot}{\today \hfill \bfseries\thepage\ of \pageref*{LastPage}}

\pagestyle{fancyplain}
\lhead[\fancyplain{}{\bfseries\thepage of \pageref{LastPage}}]
    {\fancyplain{}{\bfseries\rightmark}}
\rhead[\fancyplain{}{\bfseries\leftmark}]
    {\fancyplain{}{Paul T. Pham \hfill}}
\cfoot[]{\customfoot}
\addtolength{\headheight}{1.6pt}

\addtolength{\topmargin}{-0.75in}	% repairing LaTeX's huge margins...
\addtolength{\textwidth}{1in}	% same here....
\addtolength{\marginparwidth}{.1in}	% The word ``Memberships'' is really long below
\setlength{\headwidth}{\textwidth}
\setlength{\parindent}{0mm}	% indented paragraphs just don't make it
			   	% on a resume.  (My opinion; if you
			   	% disagree, give this whatever value you
			   	% want.)
\setlength{\textheight}{9.25in}	% more margin hacking.  I have a large
			    	% resume to fit on one page.

\fancypagestyle{firststyle}
{
   \fancyhf{}
   \fancyfoot[C]{\customfoot}
}

\begin{document}

\thispagestyle{firststyle} % no headers, but custom footers on the first page

\reversemarginpar		% this puts the margin notes on the
				% left-hand side of the resume.

{\LARGE {\bf Paul T. Pham}}
\par
\vspace{.25in}
E-mail: \href{mailto:ppham@local-box.org}{ppham@local-box.org}
\hspace*{\fill}
1620 Woodard Ave Northwest, Unit C-4
\linebreak
Phone: (206) 859-0322
\hspace*{\fill}
Olympia, WA 98502

				% address stuff.  The \hspace*{\fill} is
				% necessary to get things laid out
				% correctly.  The sizes fed to \vspace are
				% variable, depending on how much
				% whitespace you want, and how much
				% stuff you're trying to fit on a page....
\par
\vspace{.25in}
				% if the \marginpar is at the beginning
				% of the line, it loses.  *sigh*.  This
				% is a typical entry in a resume.   (I'm
				% defining an entry as something
				% important enough to have a marginal note
				% setting it off.)  Give it some space
				% with \vspace, use \par to break
				% between paragraphs, enter your text,
				% and place the \marginpar at the end.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%I\marginpar{{\bf Teaching\\ Philosophy}} am excited about teaching computer
%science using the following techniques:
%storytelling (the connection of topics using unifying themes and simple narratives),
%personal involvement (doing projects alongside students), and
%continuously gathering and responding to feedback.

%\vspace{\baselineskip}
%\par

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{\bf University of Washington (UW)}
\marginpar{{\bf Education}}
\par
Doctor of Philosophy in Computer Science \hspace*{\fill}September 2013\\
%Expected graduation date June 2013. Current GPA: 3.78/4.0\\
%\href{http://quantum.cs.washington.edu}{Quantum Computing Theory Group}\\
Thesis: \emph{Low-depth quantum architectures for factoring}.
Advised by \href{http://www.cs.washington.edu/people/faculty/aram/}{Aram Harrow}
and Dave Bacon.
\vspace{\baselineskip}
\par

{\bf Massachusetts Institute of Technology (MIT)}
\par
Master of Engineering in Electrical Engineering \& Computer Science, February 2005.\\
%Graduate GPA: 4.7/5.0\\
Thesis: \href{http://sourceforge.net/project/showfiles.php?group_id=129764&package_id=144780&release_id=307201}{\emph{A general-purpose pulse sequencer for quantum computing}}.
Advised by \href{http://feynman.mit.edu/ike/homepage/index.html}{Isaac Chuang}\\
\par
Bachelor of Science in Electrical Engineering and Computer Science, June 2004.\\
%Undergraduate GPA: 4.2/5.0
\vspace{\baselineskip}
\par
				% This is a slightly more complicated
				% example.  \vspace gets a `doublespace'
				% (1.5\baselineskip) between entries, and
				% a  `singlespace' between paragraphs of
				% an entry.
				% (1.5\baselineskip means twice the value
				% of \baselineskip).


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{\bf CodeFellows} \hfill Seattle, Washington
\marginpar{{\bf Employment \& \\ Teaching \\ Experience}}
\vspace{0.5\baselineskip}
\par
{\em Instructor}\hfill March 2015---Present

\vspace{0.5\baselineskip}
\par
\href{https://www.codefellows.org/courses/foundations-1/computer-science-and-web-development}{Foundations of Computer Science and Web Development}\hfill April 2015---Present
\vspace{0.5\baselineskip}
\par
\href{https://www.codefellows.org/courses/foundations-2/python}{Python Foundations II}\hfill March---April 2015
\vspace{0.5\baselineskip}
\par

{\bf The Evergreen State College} \hfill Olympia, Washington
\vspace{0.5\baselineskip}
\par
{\em Tenure-Track Member of the Faculty}\hfill September 2013---September 2014

\vspace{0.5\baselineskip}
\par
\href{http://ada.evergreen.edu/csf/python13f/}{Programming as a Way of Life}\hfill Fall 2013---Spring 2014
\vspace{0.5\baselineskip}
\par
\href{http://design-comp-things.org/}{Design of Computational Things}\hfill Spring 2014

\vspace{0.5\baselineskip}
\par

{\bf UW Computer Science \& Engineering Dept.} \hfill Seattle, Washington
\vspace{0.5\baselineskip}
\par
{\em Instructor}

\vspace{0.5\baselineskip}
\par
Quantum Computing for Beginners (\href{http://www.cs.washington.edu/education/courses/490q/12au/}{CSE 490Q})\hfill September 2012---Present
\par
An original course to teach the basics of quantum computing and D-Wave programming.

\vspace{0.5\baselineskip}
\par
{\em Teaching Assistant}

\vspace{0.5\baselineskip}
\par
Advanced Internet Services (\href{http://www.cs.washington.edu/education/courses/454/12wi/}{CSE 454})\hfill January 2012---March 2012
\par
Professor Oren Etzioni

\vspace{0.5\baselineskip}
\par
The Hardware/Software Interface (\href{http://www.cs.washington.edu/education/courses/351/10sp/}{CSE 351})\hfill April---June 2010
\par
Professor Gaetano Borriello

\vspace{0.5\baselineskip}
\par
Data Structures (\href{http://www.cs.washington.edu/education/courses/326/06au/}{CSE 326})\hfill September---December 2006
\par
Professor Larry Snyder

\vspace{0.5\baselineskip}
\par
Software Development Tools (\href{http://www.cs.washington.edu/education/courses/303/06sp/}{CSE 303})\hfill April---June 2006
\par
Professor Magda Balazinska

\vspace{0.5\baselineskip}
\par
Algorithms (\href{http://www.cs.washington.edu/education/courses/417/06wi/}{CSE 417})\hfill January---March 2006
\par
Professor Larry Ruzzo

\vspace{0.5\baselineskip}
\par
Discrete Structures Class (\href{http://www.cs.washington.edu/education/courses/321/05au/}{CSE 321})\hfill September---December 2005
\par
Professors Dieter Fox \& Anna Karlin
\par

\pagebreak

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{\baselineskip}
\par
\emph{A 2D nearest-neighbor quantum architecture for factoring.}
\marginpar{{\bf Publications}}\\
\textbf{P. Pham}, K.M. Svore. \hfill \url{http://arxiv.org/abs/1207.6655}\\
Reversible Computation Workshop, June 2012 \hfill Copenhagen, Denmark

\vspace{\baselineskip}
\par
\emph{Quantum compiling single-qubit gates with the Kitaev-Shen-Vyalyi procedure.}\\
\textbf{P. Pham}\\
Ph.D. qualifying examination report.

\vspace{\baselineskip}
\par
\emph{Component-based invisible computing.}\\
A. Forin, J. Helander, \textbf{P. Pham}, J. Rajendiran.\\
IEEE Realtime Embedded Systems Workshop, December 2001 \hfill London, UK

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{\baselineskip}
\par
\emph{A 2D quantum architecture for factoring in sub-quadratic depth.}
\marginpar{{\bf Posters}}\\
\textbf{P. Pham}\\
Quantum Information Processing (QIP) Conference, December 2011.

\vspace{\baselineskip}
\par
\emph{Quantum compiling with Kitaev-Shen-Vyalyi.}\\
\textbf{P. Pham}\\
Southwest Quantum Information and Technology (SQuInT), February 2011.

\vspace{\baselineskip}
\par
\emph{Adiabatic shelving to the $5D_{5/2}$ state in trapped barium ions.}\\
R. McClure, J. Booth, \textbf{P. Pham}, J. Wright, T. Noel, B. Blinov\\
Southwest Quantum Information and Technology (SQuInT), February 2011.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{\baselineskip}

\emph{Method and system for managing the execution of threads and data processing.}
\marginpar{{\bf Patents}}\\
A. Forin, J. Helander, \textbf{P. Pham}.\\
\href{http://patft.uspto.gov/netacgi/nph-Parser?Sect1=PTO2&Sect2=HITOFF&u=%2Fnetahtml%2FPTO%2Fsearch-adv.htm&r=1&p=1&f=G&l=50&d=PTXT&S1=20030233392&OS=20030233392&RS=20030233392}{U.S. Patent No. 7,246,353}\\
Filed on June 12, 2002.
Granted on July 17, 2007.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{\baselineskip}
\par
{\bf {University of Puget Sound}} \hfill Tacoma, Washington\marginpar{{\bf Invited\\ Talks}}
\par
{\em The mathematics of quantum computing} \hfill November 2013
\par
Hosted by Prof. Carl Toews.

\vspace{\baselineskip}
\par
{\bf {University of British Columbia}} \hfill Vancouver, Canada
\par
{\em Quantum architecture, compiling, and 2D factoring} \hfill September 2012
\par
Hosted by Prof. Robert Raussendorf.

\vspace{\baselineskip}
\par
{\bf {University of Innsbruck}} \hfill Innsbruck, Austria
\par
{\em Quantum architecture, compiling, and 2D factoring} \hfill July 2012
\par
Hosted by Prof. Rainer Blatt.

\vspace{\baselineskip}
\par
{\bf {University of Freiburg}} \hfill Freiburg, Germany
\par
{\em Quantum architecture, compiling, and 2D factoring} \hfill July 2012
\par
Hosted by Prof. Tobias Sch\"atz.

\vspace{\baselineskip}
\par
{\bf {University of Aarhus}} \hfill Aarhus, Denmark
\par
{\em Quantum architecture, compiling, and 2D factoring} \hfill July 2012
\par
Hosted by Prof. Michael Drewsen.

\pagebreak

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{\baselineskip}
\par
{\bf {UW Computer Science \& Engineering Dept.}} \hfill Seattle, WA\marginpar{{\bf Students\\ Mentored}}
\par

\vspace{0.5\baselineskip}
\par
\emph{Noah Siegel} \hfill September 2012---Present
\par
Improving the exponential dimensional dependence in the quantum compiling
procedure of Kitaev, Shen, Vyalyi.

\vspace{0.5\baselineskip}
\par
\emph{Andrea McCool} \hfill June 2010---Present
\par
Mapping Shor's algorithm to a nearest-neighbor 2D quantum architecture in
constant circuit depth.

\vspace{0.5\baselineskip}
\par
\emph{Jeffrey Booth, Jr.} \hfill January 2010---May 2012
\par
Honors senior thesis. Meet-in-the-middle optimizations for a quantum compiler.

\vspace{0.5\baselineskip}
\par
\emph{Harshad Petwe} \hfill June 2010---August 2011
\par
Constructing a programmable pulse generator for controlling trapped atomic
ions in quantum information processing experiments at the Max Planck Institute
for Quantum Optics.

\vspace{0.5\baselineskip}
\par
\emph{Rob McClure} \hfill January 2010---March 2011
\par
\emph{John Williams} \hfill January 2010---May 2010
\par
\emph{David Nufer} \hfill January 2010---May 2010
\par
Extending a programmable pulse generator for controlling trapped atomic
ions to perform adiabatic shelving of electron energy states in the UW
Physics Department.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{\baselineskip}

{\bf MIT ACM/IEEE Programming Competition} \hfill Cambridge, Massachusetts
\marginpar{{\bf Activities}}

{\em Contest Chair, Lead Developer, Organizer} \hfill 2001-2003
\vspace{0.5\baselineskip}
\par

\url{http://www.battlecode.org}\\
\url{http://web.mit.edu/ieee/6.370/2003/web/}\\
Created a long-running
programming competition for distributed software agents to play a
a real-time strategy game. Winning student competitors were matched with
corporate sponsors which now include
Dropbox, Blizzard Entertainment, Amazon, Google, Oracle, D.E. Shaw, and Akamai.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{\baselineskip}
\par
{\bf {Pulse Programmer}} \hfill SourceForge\marginpar{{\bf Software}}
\par
{\em Project Admin, Lead Developer} \hfill January 2005---Present
\par
\url{http://pulse-programmer.org}
\par
Built an open source reconfigurable radio-frequency signal generator
for quantum computing and quantum information processing experiments.
In use at eight experimental trapped ion research groups around the world.

\vspace{\baselineskip}
\par
{\bf {Quantum Compiler}} \hfill SourceForge, Github
\par
{\em Project Admin, Lead Developer} \hfill January 2005---Present
\par
\url{http://quantum-compiler.org}
\par
Developed an open source code in Python and NumPy to implement the
Solovay-Kitaev quantum compiling algorithm for generic, multi-qubit gates
in SU(d). Simulated the Kitaev-Shen-Vyalyi quantum compiling algorithm in
QCL and wrote code to measure its required resources. Accepted as
qualifying examination project in the UW CSE Ph.D. program.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{\baselineskip}
\par
{\bf {Max E. Gellert Fellowship}} \hfill 2005-2006\marginpar{{\bf Awards}}\\
University of Washington, College of Engineering \hfill Seattle, WA

\par

\pagebreak

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{\baselineskip}
\par
{\bf {Microsoft Research}} \hfill Seattle, WA\marginpar{{\bf Research\\ Experience}}
\par
{\em Research Intern} \hfill June---August 2011
\par
\href{http://research.microsoft.com/en-us/groups/quarc/default.aspx}{Quantum Architectures and Computation Group}
\par
Mentor: Krysta Svore
\par
Designed a 2D nearest-neighbor quantum architecture for period-finding with
depth $O(L \log L)$ for factoring an $L$-bit integer. Pending patent
application.

\vspace{\baselineskip}
\par
{\bf {University of Washington Dept. of Physics and Astronomy}} \hfill Seattle, WA
\par
{\em Graduate Research Assistant} \hfill January---July 2007, May---June 2010
\par
\href{http://depts.washington.edu/qcomp/}{Trapped Ion Quantum Computing Group}
\par
Advisor: Prof. Boris Blinov
\par
Built a programmable radio-frequency system for ion trap control including
photomultiplier tube input counting.

\par

\vspace{\baselineskip}
\par
{\bf Max Planck Institute for Quantum Optics} \hfill Garching, Germany
\par
{\em Visiting Ph.D. Student} \hfill July 2005---August 2005
\par
\href{http://www.mpq.mpg.de/qsim/}{Quantum Analog Simulation Group}
\par
Advisor: Dr. Tobias Sch\"atz
\par
Built a programmable radio-frequency system for ion trap control with phase-coherent
frequency-switching.

\par

\vspace{\baselineskip}
\par
{\bf University of Innsbruck} \hfill Innsbruck, Austria
\par
{\em Visiting Ph.D. Student} \hfill February 2005---June 2005
\par
\href{http://heart-c704.uibk.ac.at/index.html}{Quantum Optics and Spectroscopy Group}
\par
Advisor: Univ. Prof. Rainer Blatt
\par
Built a programmable radio-frequency system for ion trap control with shaped amplitudes.
\par

\vspace{\baselineskip}
\par
{\bf MIT Center for Bits and Atoms} \hfill Cambridge, Massachusetts
\par
{\em Graduate Research Assistant} \hfill September 2003---January 2005
\par
\href{http://web.mit.edu/~cua/www/quanta/}{quanta Research Group}
\par
Advisor: Prof. Isaac Chuang
\par
Designed and built instrumentation for quantum computing experiments.
\par

\vspace{\baselineskip}
\par
{\bf Microsoft Research} \hfill Redmond, WA
\par
{\em Research Intern} \hfill June 2001---September 2001
\par
\href{http://research.microsoft.com/en-us/projects/mic/default.aspx}{Invisible Computing Group}\hfill June 2003---August 2003
\par
Mentors: Alessandro Forin, Johannes Helander
\par
Added work items to the scheduler of an embedded real-time kernel.
Designed and assembled the electronics for a wireless sensor demo.

\par

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{\baselineskip}
\par
{\bf {Amazon.com}} \hfill Seattle, WA\marginpar{{\bf Work\\ Experience}}
\par
{\em Software Development Engineer} \hfill January 2008---June 2009
\par
\href{http://www.endless.com}{Endless.com Designer Shoes and Handbags}
\par
Manager: Doug Irvine
\par
Maintained a large-scale, high-availability
retail website built using Apache Tomcat, J2EE,
the Spring dependency-injection framework, jQuery, and Ajax. Implemented a
pipeline for customers to write product reviews.

\pagebreak

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{\bf Richard Weiss}
\marginpar{{\bf References}}\\
Member of the Faculty\\
The Evergreen State College\\
2700 Evergreen Parkway NW, Lab II 3260\\
Olympia, WA 98505\\
Phone: (360) 867-6871\\
E-mail: \url{weissr@evergreen.edu}\\

{\bf Aram Harrow}
Research Assistant Professor\\
University of Washington, Department of Computer Science \& Engineering\\
Box 352350, Seattle, WA 98195-2350\\
Phone: (206) 616-0733\\
E-mail: \url{aram@cs.washington.edu}\\

{\bf Gaetano Borriello}\\
Jerre D. Noe Professor of Computer Science \& Engineering\\
University of Washington, Department of Computer Science \& Engineering\\
Box 352350, Seattle, WA 98195-2350\\
Phone: (206) 685-9432\\
E-mail: \url{gaetano@cs.washington.edu}\\

{\bf Oren Etzioni}\\
Washington Research Foundation Entrepreneurship Professor of Computer Science \& Eng.\\
University of Washington, Department of Computer Science \& Engineering\\
Box 352350, Seattle, WA 98195-2350\\
Phone: (206) 685-3035\\
E-mail: \url{etzioni@cs.washington.edu}\\

{\bf Michael D. Ernst}\\
Associate Professor of Computer Science \& Engineering\\
University of Washington, Department of Computer Science \& Engineering\\
Box 352350, Seattle, WA 98195-2350\\
Phone: (206) 221-0965\\
E-mail: \url{mernst@cs.washington.edu}\\

{\bf Boris Blinov}\\
Associate Professor\\
University of Washington, Department of Physics \& Astronomy\\
Box 351560, Seattle, WA 98195-1560\\
Phone: (206) 221-3780\\
E-mail: \url{blinov@uw.edu}\\

{\bf Tobias Sch\"atz}\\
Assistant Professor\\
Max Planck Institute for Quantum Optics\\
Hans-Kopfermann-Strasse 1\\
D-85748 Garching, Germany\\
Phone: +49-89-32905-199\\
E-mail: \url{tobias.schaetz@mpq.mpg.de}\\

%{\bf Alessandro Forin}\\
%Principal Researcher\\
%Microsoft Research\\
%1 Microsoft Way\\
%Redmond, WA 98052\\
%Phone: (425) 936-1841\\
%E-mail: \url{sandrof@microsoft.com}\\

%{\bf Rainer Blatt}\\
%University Professor of Physics\\
%Institute for Experimental Physics\\
%University of Innsbruck\\
%Technikerstrasse 25/4\\
%A-6020 Innsbruck\\
%Austria\\
%Phone: +43-512-507-6302\\
%E-mail: \url{Rainer.Blatt@uibk.ac.at}\\

%{\bf Isaac Chuang}\\
%Professor\\
%Departments of Physics and Electrical Engineering \& Computer Science\\
%Massachusetts Institute of Technology\\
%77 Massachusetts Ave\\
%Boston, MA 02139\\
%Phone: (617) 253-1692\\
%E-mail: \url{ichuang@mit.edu}\\

%{\bf Doug Irvine}\\
%Software Development Manager\\
%Amazon.com\\
%701 5th Ave, Suite 1500, Seattle, WA 98104\\
%Phone: (206) 266-3154\\
%E-mail: \url{dirvine@amazon.com}\\

%{\bf Lindsay Michimoto}\\
%Graduate Program Advisor\\
%University of Washington, Department of Computer Science and Engineering\\
%Box 352350, Seattle, WA 98195-2350\\
%Phone: (206) 543-5758\\
%E-mail: \url{lindsaym@cs.washington.edu}\\

\end{document}




